Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
Filling in more writing.

\subsection{Synthesis} 
Write about how I came up with the questions, what was considered (looking at many wearable devices and possible sensors, looking through previous works, just thinking of as many as possible), and the final list.

\subsection{Validation}
Talking about the focus group here. Does this even need to happen?

\subsection{Methodology}
CHANGE THISSSS !!!!! We recruited 500 participants on December 9th, 2013 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old residing in the U.S. All participants stated that they owned a laptop or desktop computer with either an external or an internal webcam. We asked questions regarding participants' webcam use and their understanding of the purpose of the webcam LED.

>>>>

\subsection{Threat Landscape Investigation} 
(REDO) To generate the list of possible scenarios which can happen with a wearable device, we did three things. Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities. Secondly, we looked at past research in mobile devices, vision videos for wearables, and the news for possible concerns.

Write about how I came up with the questions, what was considered (looking at many wearable devices and possible sensors, looking through previous works, just thinking of as many as possible), and the final list.

Talking about the focus group here. Does this even need to happen?

\subsection{Calibrating with Existing Works}
(REDO) We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices. Mobile devices threats are well studied and the closest well-researched thing to wearable device threats.

We used a prompt similar to Fischoff's study so that we could compare our results to the ones that he got in his study, and to put more of the new technologies onto the risk/benefit map. This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies.

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios, and clarify any scenarios which were unclear (we also used this time to time the survey and make sure the formatting was clear.

\subsection{Methodology}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old. No other restrictions on participation were applier. We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.
